Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-01 analysis.Rmd
no googlesheets

```{r}
library(dplyr)
library(ggplot2)
library(googlesheets)
library(readr)
library(tidyr)
```

Get project planning sheet straight from google docs.

```{r}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup = TRUE) # Need lookup=T to initialize
project_plan_raw <- gs_read_csv(project_plan_sheet)
```

Exclude those to be excluded.

```{r}
project_plan <- project_plan_raw %>%
  filter(`include_in_final_writeup`==1) 
```

@@

passing <- c("mkeil","jreynolds","jmarias","jsalloum","ehermann",
             "jedtan", "lampinen", "salehi")
failing <- c("smraposo", "auc", "rhiac")

>>>>

```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
```

Get project planning sheet and exclude those to be excluded.

```{r}
project_plan_raw <- read_csv("data/planning_and_outcomes.csv")

project_plan <- project_plan_raw %>%
  filter(`include_in_final_writeup`==1) 
```

@@

passing <- c("mkeil","jreynolds","jmarias","jsalloum","ehermann",
              "lampinen")
failing <- c("smraposo", "auc", "rhiac", "jedtan", "salehi")

### 2016-07-01 paper/paper.Rmd
analysis
no googlesheets

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct direct replications as part of their training; but to date there is limited evidence that this proposal can result in high-quality research outputs. We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level experimental methods. By a variety of measures, these replications were successful approximately half of the time, providing an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."

@@

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(googlesheets)
library(dplyr)
library(xtable)
```

@@

In the current article, we provide evidence on this issue by reporting the results of replication projects conducted in a single class (a graduate-level experimental methods course). As part of the required work of the course, students conducted high-power, direct replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies both provide insight into the process of pedagogical replication and give evidence about the state of replicability.

@@

With respect to broader questions of meta-science, it is a challenging proposition to estimate the replicability of an entire literature [cf. @osc2015;@gilbert2016;@anderson2016]. Making such an estimate requires determining a sampling strategy, a notion of what constitutes a direct replication, what constitutes a successful replication, among many other difficult decisions. In the current work, we focus on a quantity that is easier to estimate: the probability that a graduate student can choose an article of interest in *Psychological Science* and -- in a single attempt, and within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fidelity to be able to build on it in future work. We believe that this notion of whether a piece of research supports cumulative progress is an important construct. Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is reproducible in some more abstract sense.

@@

```{r, results='asis'}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup=TRUE) # Need lookup=T to initialize
project_plan_raw <- gs_read_csv(project_plan_sheet)

@@

Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that 2/3 of these opted out projects were judged by the instructor team to have been successful replications; thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.

@@

All participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}. Note that of the `{r} nrow(ppt)` studies included in the final sample, `{r} sum(project_plan$original_on_turk=="Yes")` (`{r} round(mean(ppt$original_on_turk), digits=2)`%) were originally conducted on Mechanical Turk. All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."

@@

After Pilot B review was completed, students were given authorization to collect the full sample of participants, contingent on having made the requested change. Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework. (In one case, a student failed to complete the pre-registration but nevertheless submitted a pre-specified analysis plan to the instructors for review).

@@

For purposes of planning and analysis, we asked stuents Despite the general emphasis in meta-analytic and reproducibility efforts to aggregate a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test in studies. Often a wide variety of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution. Nevertheless, despite this interpretive difficulty, we attempted to use a single statistical test as our target for experiment planning and analysis. This test was determined by iterative discussion between the student, instructor, and TAs.

@@

## Analysis strategy

@@

.

@@

how many replications were conducted to the intended standard, how many opted out etc.

@@

## Scientific Assessment

### Indices of replicability

### Coding of previous years’ findings

>>>>

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct direct replications as part of their training; but to date there is limited evidence that this proposal can result in high-quality research outputs. We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level experimental methods. By a variety of measures, these replications were successful approximately half of the time, providing an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt. We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."

@@

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(dplyr)
library(xtable)
```

@@

In the current article, we provide evidence on this issue by reporting the results of replication projects conducted in a single class (a graduate-level experimental methods course). As part of the required work of the course, students conducted high-power, direct replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies both give evidence about the state of replicability in the field and provide insight into the process of pedagogical replication.

It is a challenging proposition to estimate the replicability of an entire literature [cf. @osc2015]. Making such an estimate requires determining a sampling strategy, a notion of what constitutes a direct replication, what constitutes a successful replication, among many other difficult decisions [@gilbert2016;@anderson2016]. In the current work, we focus on a quantity that is easier to estimate: the probability that a graduate student can choose an article of interest in *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fidelity to be able to build on it in future work. We believe that this notion of whether a piece of research supports cumulative progress is an important construct. Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is reproducible in some more abstract sense.

@@

@@

```{r, results='asis'}
project_plan_raw <- read_csv("data/planning_and_outcomes.csv")

@@

@@

All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}. Note that of the `{r} nrow(ppt)` studies included in the final sample, `{r} sum(project_plan$original_on_turk=="Yes")` (`{r} round(mean(ppt$original_on_turk), digits=2)`%) were originally conducted on Mechanical Turk. All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."

@@

After Pilot B review was completed, students were given authorization to collect the full sample of participants, contingent on having made the requested change. Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework.

@@

Despite the general emphasis in meta-analytic and reproducibility efforts to aggregate a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test in studies. Often a wide variety of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution. Nevertheless, despite this interpretive difficulty, we attempted to use a single statistical test as our target for experiment planning and analysis. This test was determined by iterative discussion between the student, instructor, and TAs.

@@

@@

@@

Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that 2/3 of these opted out projects were judged by the instructor team to have been successful replications; thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product. (In one case, a student failed to complete the pre-registration but nevertheless submitted a pre-specified analysis plan to the instructors for review).

@@

## Confirmatory analyses

### Subjective judgments of replication

What’s the subjective “replication rating” given by MCF, ES, and RH? Criterion is based on the theoretical interpretation of the original finding. (0 = non-replication, .5 is substantial hints of the same pattern or a significant but different pattern, 1 = full replication).

```{r}
mean(project_plan$replicated_TA)
```

```{r}
mean(project_plan$replicated_student, na.rm=TRUE)
```

### Significance of the key effect size

### Original ES in the confidence interval of the replication

### Bayes factor analysis

@etz2016

### Moderator analyses

Turk vs. not-turk

```{r}
project_plan %>% 
  group_by(original_on_turk) %>%
  summarise(replicated_TA = mean(replicated_TA))
```

Coding of replication fidelity

```{r}
project_plan %>% 
  group_by(fidelity) %>%
  summarise(replicated = mean(replicated_TA))
```

Open materials/data vs. not

```{r}
project_plan %>% 
  group_by(open_materials) %>%
  summarise(replicated = mean(replicated_TA))
```

Demographics

## Exploratory analysis
